\documentclass[9pt,a4paper]{article}
\usepackage[
colorlinks = true,
linkcolor = blue,
urlcolor  = hrefcolor,
breaklinks = true]{hyperref}
\usepackage[tmargin=1in,bmargin=1in,lmargin=1.25in,rmargin=1.25in]{geometry}
\usepackage{xcolor}
\usepackage{titling}
\usepackage{ragged2e}
\usepackage{graphicx}
\usepackage{enumitem}
\definecolor{hrefcolor}{RGB}{38, 66, 139}


\newcommand{\MyHorizontalLine}{\noindent\rule{\textwidth}{1.5pt}\\}
\predate{}
\postdate{}
\preauthor{}
\postauthor{}
\title{\textbf{Muhammad Usama Tayyab}}
\date{}
\author{}

\begin{document}
	\maketitle
	\vspace{-0.25in} % adjust the length to suit your aesthetic 
	\pagenumbering{gobble}
	\centering\mbox{
		 Phone$\#$ +92 322 4227287
		 $\vert$ Email: \href{mailto:usamatayyab9@gmail.com} {usamatayyab9@gmail.com}
		 $\vert$
		 Lahore, Pakistan
	}
\MyHorizontalLine
\vspace{2mm}
\begin{justify}
	Dear Hiring Team,\\ \newline
	I am a software engineer (C++ developer) with more than 4 years of experience, writing to bring to your knowledge my desire to work in your company as a software engineer, as it is a position that interests me and matches my skills. Currently I am working on a medical device which performs peritoneal dialysis of kidney patients, to diversify my knowledge in software engineering I believe your organization could be an ideal place to work at. Here is how I could contribute:
	\begin{itemize}
		\item I have experience in working on a cross platform desktop application developed in Qt/qml and C++.
		\item As a developer I have a sound understanding of developing solutions. I have a great passion for enhancing my problem solving and C++ skills.
		\item An in-depth understanding of modern C++ and STL.
		\item Great passion for learning and understanding compiler internals, optimization techniques, modern C++ standards, data structure and algorithms.
	\end{itemize}
	I consider myself a diligent professional, with solid work ethics, who ensures integrity and transparency of tasks assigned. I would welcome the chance to discuss my suitability further. Please do not hesitate to contact me on \href{usamatayyab9@gmail.com}{usamatayyab9@gmail.com}. I trust that you will give my application your careful consideration and I look forward to hearing from you in due course
\end{justify}
\end{document}